Attributions for Poverty in Post-Socialist Countries

### 2014-02-11 article2013.Rmd
Siirryin Rmarkdowniin

% Attributions for Poverty in Post-Socialist Countries[^*]
% Markus Kainu[^**];Mikko Niemelä[^***]
% December 12, 2013

[^*]:*Work in progress. See the analysis outputs at [http://muuankarski.github.io/attributions/](http://muuankarski.github.io/attributions/)

[^**]:PhD Student. Aleksanteri institute, University of Helsinki & Department of Social Research, University of Turku <a href="mailto:markuskainu@gmail.com">markuskainu@gmail.com</a>

[^***]:Senior Researcher. Social Insurance Institution of Finland, KELA a<a href="mailto:mikko.niemela@kela.fi">mikko.niemela@kela.fi</a>

```{roptsattribArticle, echo=FALSE}
opts_chunk$set(echo=FALSE,eval=TRUE,cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=12)
```

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit("article2013.Rmd")

~/.cabal/bin/pandoc article2013.md --template=../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --toc --latex-engine=xelatex -V lang=english -V papersize:a4paper -V documentclass=scrartcl -o article2013.tex
sed -i 's/begin{figure}\[htbp\]/begin{figure}\[H\]/g' article2013.tex
xelatex article2013.tex

knitpandoc_pdf("article2013")

system("~/.cabal/bin/pandoc -s article2013.md --toc --number-sections -o article2013.html")
system("~/.cabal/bin/pandoc -f markdown -t docx article2013.md -o article2013.docx --standalone --toc --number-sections")
system("~/.cabal/bin/pandoc article2013.md -o article2013.epub --standalone --toc --number-sections")

@@

\begin{abstract}
Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.
\end{abstract}

@@

![Countries used in the analysis](figure/mapplot.pdf)

@@

--------------------------------------------------------------------------------------------
Variable                          Description                                                                                                   Source
------------------------          ------------------------                                                                                      -----------
**Individual-level**

@@

Voice and Accountability          Indicators measuring the political process, civil liberties and political rights.                             World Bank
--------------------------------------------------------------------------------------------

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5,digits=1,
                    caption="Weighted population shares of dependent variable by country",),table.placement="H",
             type="latex",
             comment=FALSE, 
             include.rownames=FALSE,
             caption.placement="top",
             size="scriptsize")

@@

```{rarticleModelsSoc, results='asis', eval=TRUE}
load("data/finalModels.RData")

coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Human Deveplopment Index",
                      "Change in GDP between 2007 to 2010",
                      "Voice and Accountability")

@@

model.names.multi.A = c("SB empty",
                      "SB individual",
                      "SB contextual",
                      "SB all",
                      "IB empty",
                      "IB individual",
                      "IB contextual",
                      "IB all")

texreg(list(soc.0,soc.1,soc.Cont,soc.4,
            ind.0,ind.1,ind.Cont,ind.4),
        custom.model.names = model.names.multi.A,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        use.packages=TRUE,
        sideways=TRUE,
        scriptsize=TRUE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)

```{rarticleModelsFull, results='asis', eval=TRUE}
load("data/finalModels.RData")

@@

library(texreg)
texreg(list(soc.4,ind.4,socVsInc),float.pos="H",
       use.packages=TRUE,
       #booktabs=TRUE,
       #dcolumn=TRUE,
       scriptsize=TRUE,
       naive = TRUE,
       caption.above=TRUE,
       doctype=FALSE,
       custom.model.names = model.names.multi.2,
       custom.coef.names = coef.names.multi,
       include.pvalues=TRUE,
       caption="Logistic multilevel random intercept model for social and individual blame type of explanation")

>>>>

---
title: "Attributions for Poverty in Post-Socialist Countries"
author: [Markus Kainu & Mikko Niemelä]
date: February 11, 2014
abstract: Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.
keywords: poverty
output:
  pdf_document:
    toc: true
    highlight: zenburn
  html_document:
    toc: true
    theme: flatly
---

@@

@@

<!--
![Countries used in the analysis](figure/mapplot.pdf)
-->

@@

----------------------------
Variable                          Description                                                                                                   Source
---------                         ------------                                                                                                  -----------
**Individual-level**

@@

Voice and Accountability          Indicators measuring the political process, civil liberties and political rights.                             World Bank
----------------------------

@@

```{rattribArticleDescTbl1, results='asis', eval=TRUE, echo=FALSE, cache=TRUE, message=FALSE}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5,digits=1,
                    caption="Weighted population shares of dependent variable by country",), #table.placement="H",
             type="latex",
             comment=FALSE, 
             include.rownames=FALSE,
             caption.placement="top",
             size="scriptsize")
```

@@

```{rarticleModelsSoc, results='asis', eval=TRUE, echo=FALSE, cache=TRUE, message=FALSE}
load("data/finalModels.RData")
library(texreg)
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Human Deveplopment Index",
                      "Change in GDP between 2007 to 2010",
                      "Voice and Accountability")

@@

model.names.multi.A = c("SB empty",
                      "SB individual",
                      "SB contextual",
                      "SB all")

texreg(list(soc.0,soc.1,soc.Cont,soc.4),
        custom.model.names = model.names.multi.A,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        #use.packages=TRUE,
        #sideways=TRUE,
        scriptsize=TRUE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)
```

```{rarticleModelsInd, results='asis', eval=TRUE, echo=FALSE, cache=TRUE, message=FALSE}
load("data/finalModels.RData")
library(texreg)
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Human Deveplopment Index",
                      "Change in GDP between 2007 to 2010",
                      "Voice and Accountability")

model.names.multi.A = c("IB empty",
                      "IB individual",
                      "IB contextual",
                      "IB all")

texreg(list(ind.0,ind.1,ind.Cont,ind.4),
        custom.model.names = model.names.multi.A,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        #use.packages=TRUE,
        #sideways=TRUE,
        scriptsize=TRUE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)
```

```{rarticleModelsFull, results='asis', eval=TRUE, echo=FALSE, cache=TRUE, message=FALSE}
load("data/finalModels.RData")

@@

library(texreg)
texreg(list(soc.4,ind.4,socVsInc),
       #float.pos="H",
       #use.packages=TRUE,
       #booktabs=TRUE,
       #dcolumn=TRUE,
       scriptsize=TRUE,
       naive = TRUE,
       caption.above=TRUE,
       doctype=FALSE,
       custom.model.names = model.names.multi.2,
       custom.coef.names = coef.names.multi,
       include.pvalues=TRUE,
       caption="Logistic multilevel random intercept model for social and individual blame type of explanation")
